Simulation study in rectangular domain

### 2024-04-23 R/simulation_study/simulation_study_rect.Rmd
push results of the simulation study launched on the cluster dahu
changes in simulation study global variables
fix bug in simulation_study_rect.Rmd

```{r global variables}
#number of batch
N_BATCH=50

@@

@@

crcvm_rect_hf_ne2<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %dopar% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H0_hf))
  m$fit(method="BFGS")
  m 
}

@@

>>>>

```{r global variables}
#number of batch
N_BATCH=10

@@

p

@@

crcvm_rect_hf_ne2<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %dopar% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}

@@

p
```
